Is Archaeology a science? Insights and imperatives from 10,000 articles and a year of reproducibility reviews

### 2025-04-18 analysis/paper/paper.qmd
working on the figure

# Number of authors ------------------
boxlplot_n_authors <- 
items_df %>% 
  filter(!is.na(year)) %>% 
  ggplot(aes(1,
             log(authors_n))) +
  geom_boxplot(
               size = 1)  +
  # median for physics, from Fanelli & Glänzel Fig 2
  geom_hline(yintercept = 1.4,
             colour = "grey70") +
  geom_text_repel(data = tibble(x = 1, 
                                y = 1.4,
                                label = "p"),
                  aes(x, y, label = label),
                  bg.colour = "white", 
                  bg.r = .2, 
                  force = 0) +
  # median for soc sci, from Fanelli & Glänzel Fig 2
  geom_hline(yintercept = 0.8,
             colour = "grey70") +
  geom_text_repel(data = tibble(x = 1, 
                                y = 0.8,
                                label = "s"),
                  aes(x, y, label = label),
                  bg.colour = "white", 
                  bg.r = .2, 
                  force = 0) +
    # median for humanities, from Fanelli & Glänzel Fig 2
  geom_hline(yintercept = 0.0,
             colour = "grey70") +
  geom_text_repel(data = tibble(x = 1, 
                                y = 0.0,
                                label = "h"),
                  aes(x, y, label = label),
                  bg.colour = "white", 
                  bg.r = .2, 
                  force = 0) +
  scale_y_continuous(limits = c(0, 5)) +
  scale_x_continuous(labels = NULL) +
  theme_minimal(base_size = base_size) + 
  theme(panel.grid  = element_blank()) +
  ylab("N. of authors (ln)") +
  xlab("Collaborator group size")

# Relative title length  ----------------

>>>>

# Number of authors ------------------
boxlplot_n_authors <- 
  ggplot() +
  # boxplot of data from this study
  geom_boxplot(data = items_df %>% 
  filter(!is.na(year)),
  aes(1, log(authors_n)),
               size = 1)  +
  # boxplot of data from Fanelli & Glänzel Fig 2
  geom_boxplot(data = sim_data %>% 
  filter(Variable == "N. of authors (ln)",
         Category %in% c("h", "p", "s")),
  aes(1, Value, 
      group = Category),
  size = 1,
  colour = "grey80")  +
  # annotations from Fanelli & Glänzel Fig 2
  geom_text_repel(data = sim_data %>% 
  filter(Variable == "N. of authors (ln)",
         Category %in% c("h", "p", "s")) %>% 
  group_by(Category) %>% 
  summarise(y = median(Value)) %>% 
  mutate(label = Category),
                  aes(1, y, 
                      label = label,
                       group = Category),
                  bg.colour = "white", 
                  bg.r = .2, 
                  force = 0) +
  scale_y_continuous(limits = c(0, 5)) +
  scale_x_continuous(labels = NULL) +
  theme_minimal(base_size = base_size) + 
  theme(panel.grid  = element_blank()) +
  ylab("N. of authors (ln)") +
  xlab("Collaborator group size") 
```

```{r}
# Relative title length  ----------------
